%% Amr Abdelmaqsoud | CV
%% Compile with: pdflatex cv.tex
\documentclass[a4paper,10pt]{article}

\usepackage[margin=12mm, top=10mm, bottom=8mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{tabularx}

% Colors
\definecolor{accent}{HTML}{1A5276}
\definecolor{grey}{HTML}{555555}
\definecolor{dark}{HTML}{2D2D2D}
\definecolor{linkblue}{HTML}{2471A3}
\definecolor{lightline}{HTML}{B0B0B0}

% Hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=linkblue,
    urlcolor=linkblue,
    pdfborder={0 0 0},
}

% Section formatting
\titleformat{\section}
    {\color{accent}\bfseries\fontsize{9}{11}\selectfont\MakeUppercase}
    {}
    {0em}
    {}
    [\vspace{-0.5mm}\textcolor{lightline}{\rule{\linewidth}{0.5pt}}\vspace{0.5mm}]
\titlespacing*{\section}{0pt}{2.5mm}{1mm}

% List formatting
\setlist[itemize]{
    leftmargin=7mm,
    labelsep=2mm,
    itemsep=0.3mm,
    parsep=0pt,
    topsep=0.3mm,
    label=\textbullet,
}

% Custom commands
\newcommand{\role}[3]{%
    {\fontsize{7.8}{9.5}\selectfont\textbf{#1 | #2}}\hfill{\fontsize{7.2}{8.8}\selectfont\textit{\textcolor{grey}{#3}}}\\[0.4mm]%
}

\newcommand{\project}[1]{%
    {\fontsize{7.5}{9.5}\selectfont\textbf{#1}}\\[0.2mm]%
}

\newcommand{\skillrow}[2]{%
    \textbf{#1:} & #2 \\[0.3mm]%
}

% Body font size
\newcommand{\bodysize}{\fontsize{7.3}{9.2}\selectfont}

% No page numbers
\pagestyle{empty}

\begin{document}
\bodysize
\color{dark}

% HEADER
\begin{center}
    {\fontsize{16}{18}\selectfont\bfseries\color{black} Amr Abdelmaqsoud}\\[0.5mm]
    {\fontsize{7.5}{9.5}\selectfont\color{grey}
        \href{mailto:amr.shams2015.as@gmail.com}{amr.shams2015.as@gmail.com}
        \enspace\textbullet\enspace +20 106 365 9918
        \enspace\textbullet\enspace Cairo, Egypt \textbullet\ Open to Relocation
    }\\[0.8mm]
    {\fontsize{7.5}{9.5}\selectfont\color{linkblue}
        \href{https://github.com/Amr-Shams}{github.com/Amr-Shams}
        \enspace\textbullet\enspace
        \href{https://linkedin.com/in/amr-abdelmaqsoud-b5107519b}{linkedin.com/in/amr-abdelmaqsoud}
        \enspace\textbullet\enspace
        \href{https://shams.amr-shams2015-as.workers.dev}{shams.amr-shams2015-as.workers.dev}
    }
\end{center}

% SUMMARY
\section{Summary}
Software engineer with 3+ years of experience across backend systems, developer tooling,
and full-stack applications. Core stack: Go, Python, Java, TypeScript. Active open-source
contributor to the PostgreSQL ecosystem (pgmoneta), CNCF projects (Kubeflow, Meshery),
and WebRTC infrastructure (Pion). Ships performance-sensitive systems, workflow
orchestration engines, and tools used by real people.

% TECHNICAL SKILLS
\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{} l X @{}}
    \skillrow{Languages}{Go, Python, Java, JavaScript / TypeScript, C/C++, OCaml}
    \skillrow{Backend}{REST APIs, gRPC, Microservices, Kafka, WebSockets, Concurrency}
    \skillrow{Databases}{PostgreSQL, Neo4j, Redis}
    \skillrow{Infra}{Docker, Kubernetes, AWS (S3, EC2), Nginx, CI/CD, Prometheus, Grafana}
    \skillrow{Frontend}{React, Vue.js, Next.js, React Flow, JavaFX}
\end{tabularx}

% EXPERIENCE
\section{Experience}

\role{Software Engineer}{IKEA, Cairo}{Oct 2024 -- Nov 2025}
\begin{itemize}
    \item Built internal Go/PostgreSQL services for 1,000+ employees handling 10,000+ daily transactions; containerised and deployed on Kubernetes.
    \item Led end-to-end feature delivery, redesigning workflows to reduce manual overhead by 40\% and improve operational efficiency by 25\%.
\end{itemize}

\role{Full Stack Developer (Contract)}{Fedni, Cairo}{Nov 2024 -- Sep 2025}
\begin{itemize}
    \item Led migration from VanillaJS to React, cutting bugs by 35\% and shipping 8+ features. Built real-time collaboration via WebSockets for 50+ concurrent users.
\end{itemize}

\role{PHP Developer (Part-Time)}{CrossWorkers, Cairo}{Jun 2024 -- Nov 2024}
\begin{itemize}
    \item Migrated platform from PHP 5.6 to 7.4/Laravel, shifted frontend modules to Vue, and optimised 15+ SQL queries for 30\% faster responses.
\end{itemize}

\role{Software Engineer (Intern $\to$ Part-Time)}{Siemens, Cairo}{Jun 2023 -- Mar 2024}
\begin{itemize}
    \item Built data visualisation platform in Python/Dash aggregating real-time results from 5+ sources for 30+ engineers.
    \item Developed TinyLFU caching with custom eviction policies for internal dashboards | work that extended the internship to a part-time role.
    \item Automated reporting pipeline reducing manual analysis by 60\%.
\end{itemize}

\role{Software Engineer Intern}{Bitnine Global (Apache AGE), Remote}{Mar 2023 -- Nov 2023}
\begin{itemize}
    \item Extended Apache AGE Viewer with graph visualisation features and built a Cypher query builder for the graph database interface.
\end{itemize}

\role{Python Intern}{Master Micro, Cairo}{Jan 2023 -- Mar 2023}
\begin{itemize}
    \item Python development and testing across internal tooling projects.
\end{itemize}

% OPEN-SOURCE CONTRIBUTIONS
\section{Open-Source Contributions}
\begin{itemize}
    \item \textbf{pgmoneta (PostgreSQL)} | Full S3 backup support end-to-end (\textasciitilde 15 PRs): rebuilt upload path, extended HTTP client, optimised workflow. Mentored by senior PostgreSQL contributor.
    \item \textbf{Pion/Turn (WebRTC)} | Connection serialiser reducing CPU and memory footprint by \textasciitilde 30\% (under review).
    \item \textbf{Meshery / Kubeflow (CNCF)} | Kubernetes operators, UI fixes, and caching optimisations for Meshery operator.
    \item \textbf{Watermill} | Fixed concurrency bug with shared slices in scaled multi-threaded applications.
    \item \textbf{Other} | pg\_bulkload (config DSL adopted upstream), pgexporter, optimagic (dynamic module loading), Jitsi Meet (polling feature).
\end{itemize}

% PROJECTS
\section{Projects}

\project{Flow It | Claim Check Pattern Orchestrator}
\begin{itemize}
    \item Full-stack Go workflow engine processing 1,000+ tasks/hour. Replaced Kafka fat events with claim-check tokens, cutting server costs while keeping resilience. React Flow UI for 50+ node pipelines.
\end{itemize}

\project{Collaborative Drawing | Undo/Redo Conflict Manager}
\begin{itemize}
    \item Conflict-aware undo/redo for a shared real-time canvas (1,000+ concurrent users), based on a classic concurrency control paper. Collision resolution and memory management.
\end{itemize}

\project{Hotspot | Raycast Network Scanner Extension (\textasciitilde 800 downloads)}
\begin{itemize}
    \item macOS Raycast extension that scans local networks and identifies connected devices with IP/MAC addresses and estimated performance. Published on the Raycast Store.
\end{itemize}

\project{Blocker | Blockchain Network Debugger}
\begin{itemize}
    \item P2P debugger analysing 500+ TPS with real-time monitoring. Network simulation for testing 20+ node configurations and consensus scenarios.
\end{itemize}

\project{AOC 2025 in OCaml}
\begin{itemize}
    \item Advent of Code 2025 solutions in OCaml | picked up the language from scratch for the challenge.
\end{itemize}

% EDUCATION
\section{Education}
\textbf{B.S. Computer Engineering} | Cairo University, Jan 2025\\
\begin{itemize}
    \item Top 4 Finalist, Advanced Database Graduation Project (out of 33 teams).
\end{itemize}
\textbf{Study Abroad (Scholarship)} | San Jose State University, Spring 2023

\end{document}
